Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2023-02-05 ms/ms06_floats.tex
ENH
ENH improved ontology

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 1: Comorbidity matrix
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
\centering
%
\includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
%
\caption{Trait distance based on the Spearman correlation of colocalized eQTL beta values for different gene and samples.}
\label{fig:gwas_distance}
%
\end{figure}

@@

% full size table is table
\begin{table}[!tbp]
\centering
\scriptsize
%\hline
\csvreader[separator=tab,
tabular=crclcp{0.4\textwidth},
head,
table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Marker eQTL gene& \bfseries GWAS Categories\\\hline,
]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
{\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
\vspace{15pt}
%
\caption{Example eQTLs involved in four GWAS categories in different cytobands.
The whole list is given in the Supplementary files.
The gene marker is the eQTL gene with the highest PubMed publication count.}
\label{tab:pleitropic_variants}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 1: Comorbidity matrix
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure}[!tbp]
    \centering
%
    \includegraphics[width=\textwidth]{\floatRelativePath/plthtmp_disease_comorbidity_matrix.py/corr_inkscape.png}
%
    \caption{Trait distance based on the Spearman correlation of colocalized eQTL beta values for different genes and samples.}
    \label{fig:gwas_distance}
%
\end{figure}

@@

% full size table is table
\begin{table}[!tbp]
    \centering
    \scriptsize
%\hline
    \csvreader[separator=tab,
    tabular=crclcp{0.4\textwidth},
    head,
    table head=\bfseries Chrom. & \bfseries Pos (hg38) & \bfseries Cytoband & \bfseries RSID & \bfseries Gene marker& \bfseries GWAS Categories\\\hline,
    ]{\floatRelativePath/cmpt_count_per_rsid.py/count_per_rsid_gwas_ms.tsv}{}% use head of csv as column names
        {\csvcoli\ & \csvcolii\ & \csvcoliii\ & \csvcoliv\ & \csvcolv\ & \csvcolvi}% specify your coloumns here
%\hline
%
    \vspace{15pt}
%
    \caption{Example eQTLs involved in four GWAS categories in different cytobands.
    The gene marker is the eQTL gene with the highest PubMed publication count.
    The whole list is given in the Supplementary files.}
    \label{tab:pleitropic_variants}
\end{table}
